A fully labelled proof system for intuitionistic modal logics

### 2021-01-13 FullyLabelled/JLC/conclusion.tex
adding comments
finished all the todos

In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and generalise it to the class of logics defined by (one-sided) intuitionistic Scott-Lemmon axioms.
%
We establish that it is a valid approach to intuitionistic modal logic by proving soundness and completeness of our system, via a reductive cut elimination argument.

@@

As for more general future work, there is a real necessity of a global view on intutionistic modal logics.
%
The work of~\cite{dalmonte:grellois:olivetti:arxiv19} is a great first step in understanding them in the context of non-normal modalities and neighbourhood semantics.
%
It would be interesting to know how and where the class of logics we considered can be included in their framework.

>>>>

In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and we study it in-depth for the class of logics defined by (one-sided) intuitionistic Scott-Lemmon axioms.
\todo{The frame properties and rules considered in the paper under review are all of the geometric form,
	so it would be more correct to say that it is an in-depth study of intuitionistic modal logic for a larger
	class of geometric frame properties rather than a generalization of the results in the paper by
	Maffezioli,  Naibo and Negri .}\sonia{OK}
%
We establish that it is a valid approach to intuitionistic modal logic by proving soundness and completeness of our system, via a reductive cut elimination argument.

@@

As for more general future work, there is a real necessity of a global view on intutionistic modal logics.
%
The work of~\cite{dalmonte:grellois:olivetti:JPL2020} is a great first step in understanding them in the context of non-normal modalities and neighbourhood semantics.
%
It would be interesting to know how and where the class of logics we considered can be included in their framework.

\todo{In references, book and theses titles should be capitalized (this is not done consistently).} \marianela{book title or the chapter as well?} \sonia{OK}

\todo{DG019 change to published reference}\sonia{OK}

### 2021-01-13 FullyLabelled/JLC/introduction.tex
adding comments
finished all the todos

In order to address these two concerns we propose here to enrich usual 
labelled sequents by allowing both, relational atoms of the
form $\futs xy$ and of the form $\accs xy$. 

@@

A system similar to ours is presented
in~\cite{maffezioli:etal:synthese13}, for intuitionistic bimodal
epistemic logic. That system is also a multi-conclusion labelled system with
more than one relation. In fact, the logical rules are essentially the
same as ours, but we use a more general setting and provide deductive proof
systems for a larger class of intuitionistic modal logics, together
with an internal cut elimination procedure.

>>>>

In order to address these two concerns we follow here the approach~\cite{garg2012,maffezioli:etal:synthese13} that enriches usual  labelled sequents by allowing both, relational atoms of the form $\futs xy$ and of the form $\accs xy$ and develop it into a uniform general framework. 
%\marianela{The reviewer suggested to change the above sentence for the next one:
%	\emph{"As done earlier in the literature  on intuitionistic modal logic (cf....) we consider here
%	to enrich"} since Maffezioli, Naibo and Negri have already done this before and the next one:
%	D. Garg, V. Genovese, and S. Negri, Countermodels from sequent calculi in multi-modal	logics. LICS 2012, IEEE Computer Society, pp. 315–324, 2012. (ALREADY ADDED ON REFERENCES FILE TO USE IT IF WE CHANGE THE SENTENCE: \cite{garg2012})
%	What do you think about changing the sentence? We have already mentioned Maffezioli, Naibo and Negri's paper a few times...
%	}
\todo{add footnote}\sonia{added the reference in the text directly}

@@

A system similar to ours is presented
in~\cite{maffezioli:etal:synthese13}, for intuitionistic bimodal
epistemic logic. That system is also a multi-conclusion labelled system with
more than one relation. In fact, the logical rules are essentially the
same as ours, but we use a more general setting and provide deductive proof
systems for a larger class of intuitionistic modal logics, together
with a syntactic cut elimination procedure.
%\review{More specifically, it is not clear what the authors mean by  "internal cut elimination procedure" on the next paragraph.
%	At the beginning of the paper "internal calculi" are identified as those calculi, such as hypersequent
%	or nested calculi, that do not have explicit accessibility relations. But then in which sense it the
%	cut elimination "internal"? Is it because there are no cuts on relational atoms? This is the case
%	also for the mentioned MNN paper.  Please clarify.}
\sonia{OK}

### 2021-01-13 FullyLabelled/JLC/system.tex
more comments
adding comments
finished all the todos

In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:
\begin{equation}
  \label{eq:cut}
  \vliiinf{\labrn{cut}}{}{
    \lseq\B\Left\Right}{
    \lseq\B\Left{\Right,\labels{z}{C}}}{}{
    \lseq\B{\Left,\labels{z}{C}}{\Right}}
\end{equation}
Then we can summarize soundness, completeness, and cut
admissibility of $\labIKp$ in the following Theorem:

>>>>

In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination.
%
The cut rule has the following shape:
\begin{equation}
  \label{eq:cut}
  \vliiinf{\labrn{cut}}{}{
    \lseq\B\Left\Right}{
    \lseq\B\Left{\Right,\labels{z}{C}}}{}{
    \lseq\B{\Left,\labels{z}{C}}{\Right}}
\end{equation}

We say that a formula is \emph{provable} in $\labIKp$ (or $\labIKp+\labrn{cut}$, resp.) if for any label $\lb x$, the sequent $\SEQ \labels{x}{A}$ is derivable from only axioms using the rules in Figure~\ref{fig:labIKp} (with possible instances of $\labrn{cut}$, resp.).
%
We can summarize soundness, completeness, and cut
admissibility of $\labIKp$ in the following result.

%\review{Theorem 3.3 refers to formulas but a sequent calculus derives, in fact, sequents. In a Gentzen
%	sequent calculus a sequent can be translated into a formula, and conversely, but this is no
%	longer the case in a labelled calculus because of the labelling and the relational atoms.
%	1,4 and 2,3 refer, respectively, to formulas and to labelled formulas, so they cannot be equivalent.
%	Observe also that the paper by  Maffezioli, Naibo and Negri prove completeness wrt sequents,
%	not just wrt formulas, so it presents a more general approach.}

\todo{footnote: completeness can be proved by proof search?}\sonia{moved to end of section~\ref{sec:completeness}}

\todo{define what provable means?}\sonia{OK}
